particle_type

### 2022-04-08 particle_type.Rmd
new figures

```{r}
part_sum %>% ggplot(aes(x = name, y = value, fill = name)) + 
  geom_col() + geom_text(aes(label = percent(value/559), vjust = -0.5, position = position_dodge(width=0.9))) + ylim(0, 350) 
```

>>>>

```{r}

part_sum %>% ggplot(aes(x = name, y = value, fill = name)) + 
  geom_col() + geom_text(aes(label = percent((value/559)), #total particles is 559
                             vjust = -0.5, #above bar
                             position = position_dodge(width=0.9)) + ylim(0, 350) #makes 60% visible
```
